### 2022-09-12 dissertation/latex/packages.tex
📝 (review): First set of changes

\usepackage{acro}                   % American Mathematical Society environments}
\usepackage{amsmath}                % American Mathematical Society environments}
\usepackage{amssymb}                % American Mathematical Society Symbols
\usepackage{amsthm}                 % American Mathematical Society Theorems
% \usepackage{algorithm}            % Typeset algorithm captions
\usepackage{booktabs}
\usepackage[ruled,vlined,linesnumbered,noresetcount]{algorithm2e}
\usepackage{bbm}                    % Blackboard variants of Computer Modern Fonts
\usepackage[sorting=none]{biblatex} % BibLaTeX referencing
\usepackage{caption}                % Improved customisation of captions
\usepackage{colortbl}               % Adds colors to tables
\usepackage{datetime}               % Various date operations
\usepackage{fancyhdr}               % Add fancy headers and footers
\usepackage{float}                  % Improved interface for adding floating objects
\usepackage[T1]{fontenc}            % Allows user to select font encodings
\usepackage[bottom]{footmisc}
\usepackage[
a4paper,                            % Paper size
width=150mm,                        % Paper width
top=25mm,                           % Top margin
bottom=25mm,                        % Bottom margin
bindingoffset=6mm,                  % Binding margin
showframe                           % Adds frame to see hbox and vbox
]{geometry}                         % Easy and flexible user interface to customize page layout,
\usepackage[pdftex]{graphicx}                   
\usepackage{ifpdf}                  % Selective setup for PDF compilation
\usepackage[utf8]{inputenc}         % Set the input encoding to UTF-8
\usepackage{imakeidx}               % A general purpose hierarchical index generator
\usepackage{listings}               % Typeset sourcecode listings
\usepackage{lmodern}
\usepackage[final]{microtype}
\usepackage{pgfplots}               % Plot functions
\usepackage{relsize}
\usepackage{subcaption}             % Adds support for sub-figures and sub-captions
\usepackage{texnames}               % BIBTeX, SliTeX, AMSTeX, PiCTeX and TeXsis logos
\usepackage{todonotes}              % Add todo notes functionality
\usepackage{url}                    % URL typesetting
\usepackage{verbatim}               % Multi-line Comments

% Dependency reliant
\usepackage[
bookmarks=true,                         % (option) Build bookmarks
bookmarksnumbered=true                  % (option) Add section numbers to bookmarks
]{hyperref}
\usepackage[all]{hypcap}                % Correct PDF figure links to top of image
\usepackage[ocgcolorlinks]{ocgx2}       % Allows you to create OCGs (Optional Content Groups)

>>>>

\usepackage{acro}                   % American Mathematical Society environments}
\usepackage{amsmath}                % American Mathematical Society environments}
\usepackage{amssymb}                % American Mathematical Society Symbols
\usepackage{amsthm}                 % American Mathematical Society Theorems
\usepackage{algorithm}            % Typeset algorithm captions
\usepackage{algpseudocode}
\usepackage{booktabs}
% \usepackage[ruled,vlined,linesnumbered,noresetcount]{algorithm2e}
\usepackage{bbm}                    % Blackboard variants of Computer Modern Fonts
\usepackage[sorting=nyt, sortcites=true, maxbibnames=6, maxcitenames=1]{biblatex} % BibLaTeX referencing
\usepackage{caption}                % Improved customisation of captions
\usepackage{colortbl}               % Adds colors to tables
\usepackage{datetime}               % Various date operations
\usepackage{fancyhdr}               % Add fancy headers and footers
\usepackage{float}                  % Improved interface for adding floating objects
\usepackage[T1]{fontenc}            % Allows user to select font encodings
\usepackage[bottom]{footmisc}
\usepackage[
a4paper,                            % Paper size
width=150mm,                        % Paper width
top=25mm,                           % Top margin
bottom=25mm,                        % Bottom margin
bindingoffset=6mm,                  % Binding margin
% showframe                           % Adds frame to see hbox and vbox
]{geometry}                         % Easy and flexible user interface to customize page layout,
\usepackage[pdftex]{graphicx}                   
\usepackage{ifpdf}                  % Selective setup for PDF compilation
\usepackage[utf8]{inputenc}         % Set the input encoding to UTF-8
\usepackage{imakeidx}               % A general purpose hierarchical index generator
\usepackage{listings}               % Typeset sourcecode listings
\usepackage{lmodern}
\usepackage[final]{microtype}
\usepackage{multirow}
\usepackage{pgfplots}               % Plot functions
\usepackage{relsize}
\usepackage{subcaption}             % Adds support for sub-figures and sub-captions
\usepackage{texnames}               % BIBTeX, SliTeX, AMSTeX, PiCTeX and TeXsis logos
\usepackage{todonotes}              % Add todo notes functionality
\usepackage{url}                    % URL typesetting
\usepackage{verbatim}               % Multi-line Comments

% Dependency reliant
\usepackage[
draft=false,
bookmarks=true,                         % (option) Build bookmarks
bookmarksnumbered=true                  % (option) Add section numbers to bookmarks
]{hyperref}
\usepackage[all]{hypcap}                % Correct PDF figure links to top of image
% \usepackage[ocgcolorlinks]{ocgx2}       % Allows you to create OCGs (Optional Content Groups)

### 2022-09-12 dissertation/preamble/acknowledgements.tex
📝 (review): First set of changes

\begin{itemize}
    \item
    To my wife, Taylah. Thank you for always believing in me. You are all my
    reasons.

    \item
        To my daughter, Bean\'e. Thank you for giving life meaning.

    \item
        To my son, Aden. I can't wait to meet you!

    \item
        To my parents, Adr\'e and Engela. Thank you for making this possible.

    \item
    To my sister, Jeannie. Thank you for motivating me.

    \item
    To my supervisors, Dr.~A. Bosman, Dr.~C.W. Cleghorn and Prof.~A.P. Engelbrecht. Thank you
    for leading me.

    \item
    To my creator, God. Thank You \ldots for Everything!
\end{itemize}

@@

\begin{center}
    This project was made possible by the National Research Foundation (NRF).\\
    Thank you for the opportunity.
\end{center}

\begin{center}
    Finally, this project would not have been possible if it were not for the generous hours and hours of computational time I was given on the Center for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
\end{center}

>>>>

\begin{itemize}
    \item To my wife, Taylah. You are all my reasons.

    \item To my daughters, Bean\'e and  Aleah. Thank you for giving life meaning.

    \item To my parents, Adr\'e and Engela. Thank you for always believing in me.

    \item To my sister, Jeannie and her husband, Jaco. Thank you for always motivating me.

    \item To my supervisors, Dr. A. Bosman, Prof. C.W. Cleghorn and Prof. A.P. Engelbrecht. Thank you for not giving up on me.

    \item To my creator, God. Thank You \ldots for everything!
\end{itemize}

@@

\begin{center}
    This project was made possible by the National Research Foundation (NRF) and the Center for High Performance Computing (CHPC) Cluster at the Council for Scientific and Industrial Research (CSIR).
\end{center}

### 2022-09-12 dissertation/preamble/publication.tex
📝 (review): First set of changes

% Publication reference
\noindent
\textsf{Publication:}\\*[2.5mm]
\textsf{
    \fontsize{9}{10pt}
    \selectfont
    \textit{
        A.N. Schreuder. Training Feedforward Neural Networks with Bayesian
        Hyper-Heuristics. Master's Thesis. University of Pretoria,
        Department of Computer Science, Pretoria, South Africa.
        \monthyeardate\today
    }
}
\vspace{1cm}

% Online assets
\noindent
\textsf{Electronic, hyperlinked versions of this thesis, including
data and source code are available online at:}\\*[2.5mm]
\textsf{
    \fontsize{9}{10pt}
    \selectfont
    \url{https://github.com/arneschreuder/masters}
}
\newpage

>>>>

% Publication reference
\noindent
\textsf{Publication:}\\*[2.5mm]
\textsf{
    \fontsize{9}{10pt}
    \selectfont
    \textit{
        Schreuder, A.N. Training Feedforward Neural Networks with Bayesian
        Hyper-Heuristics. Master's Dissertation. University of Pretoria,
        Department of Computer Science, Pretoria, South Africa.
        2022
    }
}
\vspace{1cm}

% Online assets
\noindent
\textsf{Electronic, hyperlinked versions of this dissertation, including
data and source code are available online at:}\\*[2.5mm]
\textsf{
    \fontsize{9}{10pt}
    \selectfont
    \url{https://github.com/arneschreuder/masters.ai}
}
\newpage
